Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-04-24 manuscript/manuscript.tex
ms updates

>>>>

We also wanted to test whether our we see similar convergence correlations
under a more complicated, but more realistic fitness model: Gaussian
stabilizing selection. To this end we simulated both sudden optima shifts of
$\mu_\text{sudden} = \{0.1\sigma, 0.5\sigma, 1\sigma\}$ and very graduate
optima shifts of $\mu_\text{gradual} = \{\0.001\sigma, 0.01\sigma\}$ per
generation using the same two population simulation scheme described above. We
show these convergence correlations for the sudden optima shifts in
Supplementary Figure \ref{suppfig:convergence-corrs-gss}. We found that for
slow moving optima shifts, the convergence correlations are generally too weak
to be distinguished from noise reliably, so these results are excluded (but see
Supplementary Materials Section XXX).

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-convergence-corrs-gss.pdf}

  \caption{The convergence correlations across the two population line Gaussian
    stabilizing selection sudden optima shift simulations; panel rows are for
    differing line population sizes, and panel columns are the modes of
    selection across the lines (convergent, divergent, and only a single
    selected line control). All simulations have a target number of loci
    affecting the trait of $L = 1000$; line color indicates the size of the
    sudden optima shift in standard deviations of $V_S$ 95\% confidence
  intervals are also shown. Note that selection begins at generation five,
which is the reference generation; this is indicated by the split in the
lines.}

  \label{suppfig:convergence-corrs-gss}
\end{figure}

\subsubsection{Temporal Covariances and $G(t)$ under Gaussian Stabilizing Selection}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-convergence-corrs-gss.pdf}

  \label{suppfig:convergence-corrs-gss}
\end{figure}
